Replication file for the paper: A multidimensional feasibility evaluation of low-carbon scenarios

### 2021-05-04 Paper_replication_files.Rmd
Paper replication files basic version

```{r packages, include=FALSE, MESSAGE=FALSE}
pkgs<-c("vroom", "tidyverse", "plotly", "RColorBrewer", "viridis", "hrbrthemes", "here", "ggridges", "ggsci", "stringr", "cowplot","scales", "skimr", "jtools", "countrycode", "ggpmisc", "reticulate")
#install.packages(pkgs) -> please uncomment it if you don't have the required packages installed

@@

@@

#Checking for quantiles for the visualizations
carbon_95<-quantile(indicators_calculated$carbon_price_npv, c(.95), na.rm = T) 
carbon_ratio_95<-quantile(indicators_calculated$carbon_ratio, c(.95), na.rm = T)

@@

indicators_calculated<-left_join(indicators_calculated, gov_world, by=c("Year", "Scenario_ID"))
```

@@

indicators_concerns<-indicators_calculated %>%
                     group_by(Scenario_ID, Year) %>%
                     mutate(concern_gdp=ifelse(gdp_loss>=thresholds$gdp_high,3, ifelse(gdp_loss<thresholds$gdp_low,1,2))) %>%
                     mutate(concern_carbon=ifelse(carbon_price_npv>=thresholds$carbon_high&carbon_ratio>=thresholds$carbon_ratio_high,3, 
                     ifelse(carbon_ratio<thresholds$carbon_ratio_high&carbon_price_npv<=thresholds$carbon_low,1,2))) %>%
                     mutate(concern_investment=ifelse(invest_ratio>=thresholds$invest_high,3,
                                               ifelse(invest_ratio<thresholds$invest_low,1,2))) %>%
                     mutate(concern_coal=ifelse(coal_stranded2>=thresholds$coal_high,3,
                                         ifelse(coal_stranded2<thresholds$coal_low,1,2))) %>%
                     mutate(product_economic=prod(c(concern_gdp,concern_carbon,concern_investment,concern_coal), na.rm=TRUE))%>%
                     mutate(confidence_e=length(e)-sum(is.na(c(concern_gdp,concern_carbon,concern_investment,concern_coal))))%>%
                     mutate(confidence_econ=ifelse(confidence_e==0,1, ifelse(confidence_e>2,3,2)))%>%
                     mutate(concern_economic=product_economic^(1/confidence_e)) %>%
                     mutate(concern_economic=ifelse(confidence_e==0, NA, concern_economic))

@@

t<-c("concern_wind","concern_solar","concern_nuclear","concern_biomass","concern_biomass_ccs","concern_coal_ccs","concern_transport_e","concern_transport_bio")

indicators_concerns <-  indicators_concerns %>%
                        group_by(Scenario_ID, Year) %>%
                        #mutate(concern_neg_emissions=ifelse(neg_emissions>=thresholds$neg_high,3,
                        #ifelse(neg_emissions<thresholds$neg_high&neg_emissions>=thresholds$neg_low,2,1))) %>%
                        mutate(concern_wind=ifelse(wind_scale>=thresholds$wind_high, 3,
                            ifelse(wind_scale<thresholds$wind_low,1,2))) %>%
                        mutate(concern_solar=ifelse(solar_scale>=thresholds$solar_high,3,
                             ifelse(solar_scale<thresholds$solar_low,1,2))) %>%
                        mutate(concern_nuclear=ifelse(nuclear_scale>=thresholds$nuclear_high,3,
                               ifelse(nuclear_scale<thresholds$nuclear_low,1,2))) %>%
                        mutate(concern_biomass=ifelse(biomass_scale>=thresholds$biomass_high,3,
                               ifelse(biomass_scale<thresholds$biomass_low,1,2))) %>%
                        mutate(concern_biomass_ccs=ifelse(biomass_ccs_scale>=thresholds$biomass_css_high,3,
                                   ifelse(biomass_ccs_scale<thresholds$biomass_css_low,1,2))) %>%
                        mutate(concern_coal_ccs=ifelse(coal_ccs_scale>=thresholds$coal_css_high,3,
                                ifelse(coal_ccs_scale<thresholds$coal_css_low,1,2))) %>%
                        mutate(concern_transport_e=ifelse(transport_e_increase>=thresholds$tran_elec_high,3,
                                   ifelse(transport_e_increase<thresholds$tran_elec_low,1,2))) %>%
                        mutate(concern_transport_bio=ifelse(transport_bio_increase>=thresholds$tran_bio_high,3,
                                     ifelse(transport_bio_increase<thresholds$tran_bio_low,1,2))) %>% 
                        mutate(product_technological=prod(c(concern_wind,concern_solar,concern_nuclear,concern_biomass, 
                                     concern_biomass_ccs, concern_coal_ccs,concern_transport_e,concern_transport_bio),na.rm=TRUE)) %>%
                        mutate(confidence_t=length(t)-sum(is.na(c(concern_wind,concern_solar,concern_nuclear,concern_biomass, 
                                      concern_biomass_ccs, concern_coal_ccs,concern_transport_e,concern_transport_bio)))) %>%
                        mutate(concern_tech=product_technological^(1/confidence_t))%>%
                        mutate(confidence_tech=ifelse(confidence_t==0,1, ifelse(confidence_t>7,3,2))) %>%
                        mutate(concern_tech=ifelse(confidence_t==0, NA, concern_tech))

@@

indicators_concerns<-indicators_concerns %>%
    group_by(Scenario_ID, Year) %>%
    mutate(concern_livestock=ifelse(livestock_drop>=thresholds$livestock_high,3,
                                 ifelse(livestock_drop<thresholds$livestock_low,1,2))) %>%
    mutate(concern_demand=ifelse(demand_drop>=thresholds$fe_demand_high,3,
                              ifelse(demand_drop<thresholds$fe_demand_low,1,2))) %>%
    mutate(concern_transport=ifelse(demand_transport_drop>=thresholds$tran_demand_high,3,
                                 ifelse(demand_transport_drop<thresholds$tran_demand_low,1,2))) %>%
    mutate(concern_demand_re=ifelse(demand_re_drop>=thresholds$res_demand_high,3,
                                 ifelse(demand_re_drop<thresholds$res_demand_low,1,2))) %>%
    mutate(concern_demand_industry=ifelse(demand_industry_drop>=thresholds$ind_demand_high,3,
                                       ifelse(demand_industry_drop<thresholds$ind_demand_low,1,2))) %>%
    mutate(concern_forest=ifelse(forest_increase>=thresholds$forest_high,3,
                              ifelse(forest_increase<thresholds$forest_low,1,2))) %>%
    mutate(concern_pasture=ifelse(pasture_drop>=thresholds$pasture_high,3,
                               ifelse(pasture_drop<thresholds$pasture_low,1,2))) %>%
    mutate(product_social=prod(c(concern_livestock,concern_demand,concern_transport,concern_demand_re,
                              concern_demand_industry,concern_forest,concern_pasture),na.rm=TRUE)) %>%
    mutate(confidence_s=length(s)-sum(is.na(c(concern_livestock,concern_demand,concern_transport,concern_demand_re,
                                      concern_demand_industry,concern_forest,concern_pasture)))) %>%
    mutate(concern_social=product_social^(1/confidence_s))%>%
    mutate(confidence_soc=ifelse(confidence_s==0,1, ifelse(confidence_s>5,3,2))) %>%
    mutate(concern_social=ifelse(confidence_s==0, NA, concern_social))

#overall feasibility concerns
indicators_concerns<-indicators_concerns %>%
                     group_by(Scenario_ID, Year) %>%
                     mutate(concern_overall=prod(c(concern_governance,concern_economic,concern_tech, concern_social)^(1/4), na.rm = T)) %>%
                     mutate(concern_overall=ifelse(confidence_t==0&confidence_s==0&confidence_e==0, NA, concern_overall)) %>%
                     mutate(confidence_o=confidence_e+confidence_t+confidence_s) %>%
                     mutate(confidence_overall=ifelse(confidence_o>14,3,
                                               ifelse(confidence_o<5,1,2)))

@@

>>>>

```{r packages, include=FALSE, MESSAGE=FALSE}
pkgs<-c("vroom", "tidyverse", "plotly", "RColorBrewer", "viridis", "hrbrthemes", "here", "ggridges", "ggsci", "stringr", "cowplot","scales", "skimr", "jtools", "countrycode", "ggpmisc", "reticulate", "ggrepel")
#install.packages(pkgs) -> please uncomment it if you don't have the required packages installed

@@

## Data preparation

@@

@@

indicators_calculated<-left_join(indicators_calculated, gov_world, by=c("Year", "Scenario_ID"))

#write.csv(indicators_calculated,here("input", "indicators_calculated.csv"), row.names = F)

@@

indicators_concerns<-indicators_calculated %>%
                     group_by(Scenario_ID, Year) %>%
                     mutate(concern_gdp=ifelse(gdp_loss>=thresholds$gdp_high,3, ifelse(gdp_loss<thresholds$gdp_low,1,2))) %>%
                     mutate(concern_carbon=ifelse(carbon_price_npv>=thresholds$carbon_high&carbon_ratio>=thresholds$carbon_ratio_high,3, 
                     ifelse(carbon_ratio<thresholds$carbon_ratio_high&carbon_price_npv<=thresholds$carbon_low,1,2))) %>%
                     mutate(concern_investment=ifelse(invest_ratio>=thresholds$invest_high,3,
                                ifelse(invest_ratio<thresholds$invest_high&invest_ratio>=thresholds$invest_low,2,1))) %>%
                     mutate(concern_coal=ifelse(coal_stranded2>=thresholds$coal_high,3,
                          ifelse(coal_stranded2<thresholds$coal_high&coal_stranded2>=thresholds$coal_low,2,1))) %>%
                     mutate(product_economic=prod(c(concern_gdp,concern_carbon,concern_investment,concern_coal), na.rm=TRUE))%>%
                     mutate(confidence_e=length(e)-sum(is.na(c(concern_gdp,concern_carbon,concern_investment,concern_coal))))%>%
                     mutate(confidence_econ=ifelse(confidence_e==0,1, ifelse(confidence_e>2,3,2)))%>%
                     mutate(concern_economic=product_economic^(1/confidence_e)) %>%
                     mutate(concern_economic=ifelse(confidence_e==0, NA, concern_economic))

@@

indicators_concerns <-  indicators_concerns %>%
                        group_by(Scenario_ID, Year) %>%
                        #mutate(concern_neg_emissions=ifelse(neg_emissions>=thresholds$neg_high,3,
                        #ifelse(neg_emissions<thresholds$neg_high&neg_emissions>=thresholds$neg_low,2,1))) %>%
                        mutate(concern_wind=ifelse(wind_scale>=thresholds$wind_high, 3,
                            ifelse(wind_scale<thresholds$wind_high&wind_scale>=thresholds$wind_low,2,1))) %>%
                        mutate(concern_solar=ifelse(solar_scale>=thresholds$solar_high,3,
                             ifelse(solar_scale<thresholds$solar_high&solar_scale>=thresholds$solar_low,2,1))) %>%
                        mutate(concern_nuclear=ifelse(nuclear_scale>=thresholds$nuclear_high,3,
                               ifelse(nuclear_scale<thresholds$nuclear_high&nuclear_scale>=thresholds$nuclear_low,2,1))) %>%
                        mutate(concern_biomass=ifelse(biomass_scale>=thresholds$biomass_high,3,
                               ifelse(biomass_scale<thresholds$biomass_high&biomass_scale>=thresholds$biomass_low,2,1))) %>%
                        mutate(concern_biomass_ccs=ifelse(biomass_ccs_scale>=thresholds$biomass_css_high,3,
                                   ifelse(biomass_ccs_scale<thresholds$biomass_css_high&biomass_ccs_scale>=thresholds$biomass_css_low,2,1))) %>%
                        mutate(concern_coal_ccs=ifelse(coal_ccs_scale>=thresholds$coal_css_high,3,
                                ifelse(coal_ccs_scale<thresholds$coal_css_high&coal_ccs_scale>=thresholds$coal_css_low,2,1))) %>%
                        mutate(concern_transport_e=ifelse(transport_e_increase>=thresholds$tran_elec_high,3,
                                   ifelse(transport_e_increase<thresholds$tran_elec_high&transport_e_increase>=thresholds$tran_elec_low,2,1))) %>%
                        mutate(concern_transport_bio=ifelse(transport_bio_increase>=thresholds$tran_bio_high,3,
                                     ifelse(transport_bio_increase<thresholds$tran_bio_high&transport_bio_increase>=thresholds$tran_bio_low,2,1))) %>% 
                        mutate(product_technological=prod(c(concern_wind,concern_solar,concern_nuclear,concern_biomass, 
                                     concern_biomass_ccs, concern_coal_ccs,concern_transport_e,concern_transport_bio),na.rm=TRUE)) %>%
                        mutate(confidence_t=length(t)-sum(is.na(c(concern_wind,concern_solar,concern_nuclear,concern_biomass, 
                                      concern_biomass_ccs, concern_coal_ccs,concern_transport_e,concern_transport_bio)))) %>%
                        mutate(concern_tech=product_technological^(1/confidence_t))%>%
                        mutate(confidence_tech=ifelse(confidence_t==0,1, ifelse(confidence_t>7,3,2))) %>%
                        mutate(concern_tech=ifelse(confidence_t==0, NA, concern_tech))

@@

indicators_concerns<-indicators_concerns %>%
    group_by(Scenario_ID, Year) %>%
    mutate(concern_livestock=ifelse(livestock_drop>=thresholds$livestock_high,3,
                                 ifelse(livestock_drop<thresholds$livestock_high&livestock_drop>=thresholds$livestock_low,2,1))) %>%
    mutate(concern_demand=ifelse(demand_drop>=thresholds$fe_demand_high,3,
                              ifelse(demand_drop<thresholds$fe_demand_high&demand_drop>=thresholds$fe_demand_low,2,1))) %>%
    mutate(concern_transport=ifelse(demand_transport_drop>=thresholds$tran_demand_high,3,
                                 ifelse(demand_transport_drop<thresholds$tran_demand_high&demand_transport_drop>=thresholds$tran_demand_low,2,1))) %>%
    mutate(concern_demand_re=ifelse(demand_re_drop>=thresholds$res_demand_high,3,
                                 ifelse(demand_re_drop<thresholds$res_demand_high&demand_re_drop>=thresholds$res_demand_low,2,1))) %>%
    mutate(concern_demand_industry=ifelse(demand_industry_drop>=thresholds$ind_demand_high,3,
                                       ifelse(demand_industry_drop<thresholds$ind_demand_high&demand_industry_drop>=thresholds$ind_demand_low,2,1))) %>%
    mutate(concern_forest=ifelse(forest_increase>=thresholds$forest_high,3,
                              ifelse(forest_increase<thresholds$forest_high&forest_increase>=thresholds$forest_low,2,1))) %>%
    mutate(concern_pasture=ifelse(pasture_drop>=thresholds$pasture_high,3,
                               ifelse(pasture_drop<thresholds$pasture_high&pasture_drop>=thresholds$pasture_low,2,1))) %>%
    mutate(product_social=prod(c(concern_livestock,concern_demand,concern_transport,concern_demand_re,
                              concern_demand_industry,concern_forest,concern_pasture),na.rm=TRUE)) %>%
    mutate(confidence_s=length(s)-sum(is.na(c(concern_livestock,concern_demand,concern_transport,concern_demand_re,
                                      concern_demand_industry,concern_forest,concern_pasture)))) %>%
    mutate(concern_social=product_social^(1/confidence_s))%>%
    mutate(confidence_soc=ifelse(confidence_s==0,1, ifelse(confidence_s>5,3,2))) %>%
    mutate(concern_social=ifelse(confidence_s==0, NA, concern_social))

#overall feasibility concerns
indicators_concerns<-indicators_concerns %>%
                     group_by(Scenario_ID, Year) %>%
                     mutate(concern_overall=prod(c(concern_governance,concern_economic,concern_tech, concern_social)^(1/4), na.rm = T))

@@

```{r aggregation_dimensions,include=FALSE, MESSAGE=FALSE}

feasibility_agg<-indicators_concerns %>%
                 filter(Year>2020) %>%
                 ungroup() %>%
                 select(c(Scenario_ID)|starts_with("concern")) %>%
                 group_by(Scenario_ID) %>%
                 summarise_all(geom_mean)

tem_category<-indicators_concerns %>%
              filter(Year==2030) %>%
              ungroup() %>%
              select(Scenario_ID, category, SSP_family)

feasibility_agg<-left_join(feasibility_agg, tem_category, by="Scenario_ID")

agg_1.5<-  feasibility_agg %>%
           filter(category %in% below_1.5) %>%
           filter(SSP_family==2) %>%
           select(Scenario_ID, concern_overall, concern_tech, concern_economic, concern_social, concern_governance) %>%
           rename(Overall=concern_overall) %>%
           rename(Technology=concern_tech) %>%
           rename(Economic=concern_economic) %>%
           rename(`Socio-cultural`=concern_social) %>%
           rename(Institutional=concern_governance) %>%
           pivot_longer(-c(Scenario_ID), names_to = "dimension", values_to = "feasibility_value" )

#Preparing data for the overviews over time

time_1.5<- indicators_concerns %>%
           filter(category %in% below_1.5) %>%
           filter(SSP_family==2) %>%
           select(c(Scenario_ID, Year, category)|starts_with("concern")) %>%
           rename(Overall=concern_overall) %>%
           rename(Technology=concern_tech) %>%
           rename(Economic=concern_economic) %>%
           rename(`Socio-cultural`=concern_social) %>%
           rename(Institutional=concern_governance) %>%
           pivot_longer(-c(Scenario_ID, Year, category), names_to = "dimension", values_to = "feasibility_value" )

meta_policy<-meta_policy %>%
            unite("Scenario_ID", Model:Scenario, remove = TRUE) %>%
            mutate(policy_simple=
                     ifelse(grepl('P2', Policy_category), "P2",
                          ifelse(grepl('P3',Policy_category), "P3",
                                Policy_category)))

time_1.5<-left_join(time_1.5, meta_policy, by="Scenario_ID")

time_all<- indicators_concerns %>%
           filter(SSP_family==2) %>%
           select(c(Scenario_ID, Year, category)|starts_with("concern")) %>%
           rename(Overall=concern_overall) %>%
           rename(Technology=concern_tech) %>%
           rename(Economic=concern_economic) %>%
           rename(`Socio-cultural`=concern_social) %>%
           rename(Institutional=concern_governance) %>%
           pivot_longer(-c(Scenario_ID, Year, category), names_to = "dimension", values_to = "feasibility_value" )

#Preparing data for the marker scenarios

overall_ips<-indicators_concerns %>%
             select(Model, Scenario, Year, concern_overall, concern_governance, concern_social, concern_tech, concern_economic)

overall_ips<-left_join(overall_ips, marker_set, by=c("Scenario", "Model"))

overall_ips<-overall_ips %>%
             filter(!is.na(marker))

## Figures in the main paper

```{r Figure2, echo=FALSE, warning=F, include=TRUE, MESSAGE=F, fig.width=14, fig.height=10,fig.cap="Aggregation over feasibility dimensions", fig.align="center", fig.topcaption=TRUE}

violin<-agg_1.5 %>%
  rename(`Feasibility concerns`=feasibility_value) %>%
  drop_na() %>%
  ggplot( aes(x=`Feasibility concerns`, y=dimension, fill=stat(x)))+
  geom_density_ridges_gradient(scale = 1,  
                               jittered_points = TRUE,
    position = position_points_jitter(height = 0),
    point_shape = '_', point_size = 3, point_alpha = 1) +
  scale_fill_gradient(low="#4DBBD5FF", high="#E64B3599", name = "Feasibility concerns")+
  theme_ipsum() +
  ggtitle("Feasibility Concerns (2020-2100) - SSP2 - All below 1.5 C") +
  xlab("Increasing Feasibility Concerns")+
  ylab("")+
  scale_y_discrete(limits=c("Technology","Economic","Socio-cultural","Institutional", "Overall"))+
  coord_flip()+
  theme(axis.title.y = element_text(size=18), axis.title.x = element_text(size=16))+
  theme(axis.text.x = element_text(size=20, face = "bold"), axis.title.y = element_text(size=20), legend.text = element_text(size = 20))

violin

ggsave(here("figures", "figure2_paper.png"), units="in", width=16, height=10, dpi=300)

```{r Figure3, echo=FALSE, warning=F, include=TRUE, MESSAGE=F, fig.width=14, fig.height=10,fig.cap="Aggregation over feasibility dimensions", fig.align="center", fig.topcaption=TRUE}

plot_region<-region_indicators %>%
  filter(Year>2010) %>%
  filter(category %in% below_1.5) %>%
  filter(SSP_pred==2) %>%  
  ggplot(aes(x=Year, y=concern_governance, colour=Region, fill=Region))+
  theme(text = element_text(size = 14), angle=90)+
  stat_smooth(size=2, span=0.5, se=F)+
  theme_ipsum()+ 
   xlab("")+
  ylab("Increasing Feasibility Concerns")+
    scale_color_uchicago() +
    scale_fill_uchicago()+
     theme(axis.title.y = element_text(size=20), legend.text = element_text(size = 20), legend.position = c(0.8,0.8))+
  ggtitle("Institutional Feasibility Concerns - SSP2 - Reaching 1.5C - Across Regions")

plot_region

ggsave(here("figures", "figure3_paper.png"), units="in", width=14, height=7, dpi=300)

```{r Figure4, echo=FALSE, warning=F, include=TRUE, MESSAGE=F, fig.width=14, fig.height=10,fig.cap="Aggregation over feasibility dimensions", fig.align="center", fig.topcaption=TRUE}

plot_category<-time_all %>%
  rename(`Level of concern`=feasibility_value) %>%
  filter(Year>2010) %>%
  filter(category!="no-climate-assessment") %>%
  filter(category!="Above 2C") %>%
  filter(dimension=="Overall") %>%
  mutate(category=factor(category,levels=c("1.5C low overshoot", "1.5C high overshoot","Lower 2C", "Higher 2C"))) %>%
  drop_na() %>%
  ggplot(aes(x=Year, y=`Level of concern`, color=category, fill=category))+
  geom_smooth(size=2, span=0.4, se=F)+
  theme_ipsum() +
  ylab("Increasing Feasibility Concerns")+
  xlab("")+
  scale_color_manual(values = c("#00A08799",
                                "#4DBBD599",
                                "#8491B499",
                                "#F39B7F99",
                                "#E64B3599"),
                     breaks = c("Below 1.5C", "1.5C low overshoot", "1.5C high overshoot","Lower 2C", "Higher 2C")) +
   scale_fill_manual(values = c("#00A08799",
                                "#4DBBD599",
                                "#8491B499",
                                "#F39B7F99",
                                "#E64B3599"),
                     breaks = c("Below 1.5C", "1.5C low overshoot", "1.5C high overshoot","Lower 2C", "Higher 2C"))+
   ylim(1, 1.35)+
     theme(axis.title.y = element_text(size=20), legend.text = element_text(size = 15), legend.position = c(0.8,0.8))+
  labs(fill = "Climate categories", color="Climate categories")

 plot_delay<-time_1.5 %>%
  rename(`Level of concern`=feasibility_value) %>%
  filter(Year>2010) %>%
  filter(category!="Below 1.5C") %>%
  drop_na() %>%
   filter(policy_simple!="P???") %>%
   filter(dimension=="Overall") %>%
  ggplot(aes(x=Year, y=`Level of concern`, colour=policy_simple, label=Scenario_ID, fill=policy_simple))+
  stat_smooth(size=2, se=F, span=0.5)+
  theme_ipsum()+ 
  xlab("")+
  scale_color_manual(values = c( "#00A08799",
                                "gray"),name="Policy category", 
                      labels=c("Immediate Policy Action (2020)", "Delayed Policy Action (2030)"))+
  scale_fill_manual(values = c("#00A08799",
                                "gray"), 
                      name="Policy category", 
                      labels=c("Immediate Policy Action (2020)", "Delayed Policy Action (2030)"))+
  ylim(1,1.5)+
  ylab("")+
  theme(axis.title.y = element_text(size=20), legend.text = element_text(size = 15), legend.position = c(0.8,0.8))

plot_time_trade_off<-plot_grid(plot_category, plot_delay, labels = "AUTO" )

plot_time_trade_off

ggsave(here("figures", "figure4_paper.png"), units="in", width=14, height=7, dpi=300)
```

```{r Figure5, echo=FALSE, warning=F, include=TRUE, MESSAGE=F, fig.width=14, fig.height=10,fig.cap="Aggregation over feasibility dimensions", fig.align="center", fig.topcaption=TRUE}

 plot_ips<-overall_ips %>%
  filter(Year>2010) %>%
  mutate(ip_label=ifelse(Year==2100,marker, NA)) %>%
  mutate(marker=ifelse(marker=="LED", "LED/P1", marker)) %>%
  mutate(marker=ifelse(marker=="S1", "S1/P2", marker)) %>%
  mutate(marker=ifelse(marker=="S2", "S2/P3", marker)) %>%
  mutate(marker=ifelse(marker=="S5", "S5/P4", marker)) %>%
  mutate(ip_label=ifelse(ip_label=="LED", "LED/P1", ip_label)) %>%
  mutate(ip_label=ifelse(ip_label=="S1", "S1/P2", ip_label)) %>%
  mutate(ip_label=ifelse(ip_label=="S2", "S2/P3", ip_label)) %>%
  mutate(ip_label=ifelse(ip_label=="S5", "S5/P4", ip_label)) %>%

  ggplot(aes(x=Year, y=concern_overall, colour=marker, linetype=marker))+
  geom_smooth(size=2, span=0.5)+
  scale_color_manual(values = c("LED/P1" = "#00A087FF", "S1/P2" = "#4DBBD5FF", 
                                 "S2/P3"="#8491B4FF", "S5/P4"="#F39B7FFF"))+
  geom_text_repel(aes(label=ip_label),
    force             = 3,
    nudge_x           = 0.30,
    direction         = "y",
    hjust             = 0,
    segment.size      = 0.6,
    segment.curvature = -0.3)+
    ylim(1,1.7)+
    theme_ipsum()+ 
    xlab("")+
    ylab("Increasing feasibility concerns")+
   scale_x_continuous(breaks=seq(2020,2100,10))+
  theme(axis.title.y = element_text(size=18), axis.title.x = element_text(size=16), legend.position="none")

plot_ips

ggsave(here("figures", "figure5_paper.png"), units="in", width=10, height=5, dpi=300)
